---
title: "Drake demo"
author: "Karthik Ram"
output: html_document
---

```{r setuppackagesreport, echo = FALSE}
suppressPackageStartupMessages(library(drake))
suppressPackageStartupMessages(library(Ecdat))
knitr::opts_chunk$set(
  collapse = TRUE,
  fig.width = 7,
  fig.height = 4
)
```

This small data analysis project explores some trends in R package downloads over time. The datasets are downloaded using the [cranlogs package](https://github.com/metacran/cranlogs).

```{r cranlogsintrovignette}
library(cranlogs)
cran_downloads(packages = "dplyr", when = "last-week")
```


# Results

We look at download trends in the following packages.

```{r reportlibdrakepkgs}
library(drake)
readd(package_list) # see also loadd() # nolint
```

Using the [cranlogs package](https://github.com/metacran/cranlogs), we calculate the mean number of downloads for each package from the RStudio CRAN mirror. We show these averages for the last month,

```{r reportavgrecent}
readd(averages_recent)
```

and from November 1 to December 1 in 2016.

```{r reportavgolder}
readd(averages_older)
```

We visualize the daily downloads from the last month,

```{r reportplotrecent}
readd(plot_recent)
```

and from November 1 to December 1 in 2016.

```{r reportplotolder}
readd(plot_older)
```
